% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{0pt} % allow room for 2-line header
\setlength{\headsep}{0pt}  % space between header and text
\setlength{\headheight}{0pt} % allow room for 2-line header
\usepackage[a4paper,vmargin={10mm,0mm},hmargin={15mm,15mm}]{geometry}
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it M. SHAN}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header
\name{\Large Mengfan (Fox) \underline{SHAN}\\[12pt]}% the \\[12pt] adds a blank line after name

\address{{\bf Address:} 466 Tianbao Road, Shanghai, 200086 \hspace{0.25in}  {\bf Tel:} 18017661124 \hspace{0.25in}  {\bf   Email:} dd.famous@gmail.com}

\begin{resume}
\section{{WORKING EXPERIENCE}}\label{sec:working-experience}
\vspace{-10pt}
\hrulefill\\

\vspace{-20pt}
{\bf Block}, Shanghai \hfill Since May, 2021 \\
I joined Ads \& Growth Team, Afterpay in 2021 and transitioned to Cash, Block in 2022.
My responsibilities were designing and implementing Martech Data Platform,
including data infrastructures \& integrations, data pipelines \& data-driven services.
During my time at work, I took the initiative to consolidate internal/external data and construct the Martech Data Platform.
This platform encompassed various essential components, including data integration, data processing, and the provision of diverse data services, catering to the specific requirements of downstream operations.
These services included data insights, a user data platform, and user engagement tools, ensuring seamless access and utilization of valuable information for our team's success.

\vspace{-15pt}
{\bf Shuhe Group}, Shanghai \hfill April, 2019 ~ April, 2021 \\
Leading the Data Platform Team at Shanghai's Shuhe Group.
My role included designing, developing and optimizing BigData Platform,
collaborating with both the Data Warehouse and Data Application Teams to ensure high availability.
The architecture of the data platform has undergone a transformative journey,
starting from an on-premise setup and gradually transitioning to cloud-based infrastructure.
This evolution involved the migration of data to the cloud, leading to the ultimate achievement of
a robust and comprehensive data middle platform.

\vspace{-15pt}
{\bf Works Applications}, Shanghai \hfill August, 2016 ~ April, 2019\\
As Team Leader of EDP2 (Base Technologies Div) at Works Applications.
I oversaw the development of a platform for enterprise applications on the cloud.
This included managing a server for job assignments and a Hadoop/Spark cluster for job execution.

\vspace{-12pt}
\section{{PROJECTS}}\label{sec:projects}
\vspace{-10pt}
\hrulefill\\
{\bf Eligibility Service, Block} \\
I designed and implemented Eligibility Service, a new, dynamic audience targeting service
to significantly scale Boost to all types of incentive, 
to highly reduce operational overhead for Boost set-up
and to improve reporting processes of Boost.
Kotlin, Armeria, DynamoDB, antlr4, Snowflake

Design Doc & Review
Project Management
Implementation
Maintain and monitor

\vspace{-10pt}
{\bf CustomerIQ, Block} \\
I designed and implemented the service and related data pipeline jobs of CustomerIQ, a generic Customer Data Platform.
CustomerIQ integrated data from various Clouds/Platforms and projecting  customer attributes across multiple scenarios optimised for boost targeting and ad personalisation.
Its design promoted independent addition of attributes/traits enhancing marketing effectiveness.
Kotlin, DynamoDB, Snowflake, Airflow

\vspace{-10pt}
{\bf Insight Service, Block}\\
Design and implement data infrastructures, pipelines, data quality check system and the data service for MarketplaceIQ \& AfterpayIQ,
a self-serving insight product for over 6000 merchants.
Our integrated insight service leverages data from various dimensions and utilizes AI to analyze reports for 6000 merchants.
This project steps towards building a closed-loop attribution system, unlocking the potential of our first-party data, and enables data-driven merchant decisions.
Clickhouse, Kylin, Spark, Hive, DynamoDB, OpenAI

\vspace{-10pt}
{\bf Data Mid-Platform, Shuhe} \\
Design the architecture and the migration plan of Data on Cloud.
The BigData infra was migrated from On-Promise to AWS EMR, from AWS to AliCloud and finally Data Mid-Platform.
To minimize migration impact and downtime to business,
I needed to be compatible with changes, to fix bugs on opensource components (HDFS-9406, HIVE-19994, etc)
and to provide all kinds of automation tools for migration and further management.
Cloudera, AWS EMR, S3, Ali EMR, OSS, Dataphin


\vspace{-10pt}
{\bf FeatureHub, Shuhe} \\
FeatureHub is a platform managing and providing features, for training models and online-prediction. 
Unlike traditional feature platforms, which focus on data processing, 
FeatureHub provides processed data for both online and offline services with the unified calibre. 
It provides real time features for online services with low latency, as well as historical data for training.
HBase, Flink, Hive


\vspace{-12pt}
\section{SKILLS}\label{sec:skills}
\vspace{-10pt}
\hrulefill\\
{\sl Languages:} Java, kotlin, python, Ansible, shell\\
{\sl Middleware:} Clickhouse, Kylin, Hive, HBase, Hadoop, Spark, Flume, Flink, Zookeeper, Kafka, neo4j, HugeGraph\\
{\sl Skills:} AWS, Aliyun, Snowflake


\vspace{-12pt}
\section{{EDUCATIONS}}\label{sec:educations}
\vspace{-10pt}
\hrulefill\\
{\bf Nanjing University}, Nanjing \hfill  09/2010 - 06/2016 \\
{\sl Ph.D. in Computer Software and Theory}, Department of Computer Science and Technology\\
{\bf University of Minnesota, Twin Cities}, MN \hfill 10/2014 - 10/2015 \\
{\sl Visiting Scholar supervised by Prof. Tian He}, Department of Computer Science and Engineering\\
{\bf Nanjing University}, Nanjing  \hfill 09/2006 - 06/2010 \\
{\sl Bachelor}, Department of  Computer Science and Technology\\

\vspace{-20pt}
\section{{REPOSITORIES}}\label{sec:repositories}
\vspace{-10pt}
\hrulefill\\
{\bf GitHub} \hfill https://github.com/ddfamou

\end{resume}
\end{document}
